### 2016-09-11 sec5_spm.tex
Further revise
Squeezed everything into 12 pages..

\begin{figure*}[t]
\centering
\includegraphics[width=0.85\textwidth]{spm.eps}
\vspace{-0.5em}
\caption{Star Partitioning and ApRiori Enumerator (SPARE). (a) Aggregated graph $G_A$ generated from Figure 1. (b) Five star partitions are generated from $G_A$. Star IDs are circled, vertexes and inverted lists are in the connected tables.
(c) Apriori Enumerator with various pruning techniques.}
\label{fig:star_partition}
\end{figure*}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{star-alt.eps}
\vspace{-0.5em}
\caption{Star partitioning with different vertex orderings.}
\label{fig:star-alt}
\end{figure}

@@

The maximal $G$-connected subsequence has the following two properties:
\begin{lemma}\label{lemma:union-property}
Suppose $\{T_1,T_2,\ldots,T_m\}$ is the set of all maximal $G$-connected subsequences of $T$, we have (1) $T_i\cap T_j=\emptyset$ for $i\neq j$ and (2) $T_1\cup T_2\cup\ldots\cup T_m=T$.
\end{lemma}
\begin{proof}
 \vspace{-0.5em}
We assume $T_i\cap T_j\neq \emptyset$. Let $T_i=(T_i[1], T_i[2],\ldots,T_i[p])$ and $T_j= (T_j[1], T_j[2],\ldots,T_j[n])$. Suppose $T[x]$ is a timestamp occurring in both $T_i$ and $T_j$. Let $T[y]=\min\{T_i[1],T_j[1]\}$, i.e., the minimum timestamp of $T_i[1]$ and $T_j[1]$ occurs at the $y$-th position of sequence $T$. Similarly, we assume $T[z]=\max\{T_i[p], T_j[n]\}$. Apparently, the two subsequences $T[y:x]$ and $T[x:z]$ are $G$-connected because $T_i$ and $T_j$ are both $G$-connected. Then, sequence $(T_y,\ldots,T_x,\ldots,T_z)$, the superset of $T_i$ and $T_j$, is also $G$-connected. This contradicts with the assumptions that $T_i$ and $T_j$ are maximal $G$-connected subsequences.

To prove (2), we assume $\cup_{i=1}^{i=m} T_i$ does not cover all the timestamps in $T$. Then, we can find a subsequence $T'=T[x:x+t]$ such that $T[x-1]\in T_a$ $(1\leq a\leq m)$, $T[x+t+1]\in T_b$ $(1\leq b\leq m)$ and all the timestamps in $T'$ is not included in any $T_i$. Let $g'=\min\{T[x]-T[x-1], T[x+t+1]-T[x+t]\}$. If $g'\leq G$, then it is easy to infer that $T_a$ or $T_b$ is not a maximal $G$-connected subsequence because we can combine it with $T[x]$ or $T[x+t]$  to a form superset which is also $G$-connected. If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in$\cup_{i=1}^{i=m} T_i$. Both cases lead to contradictions.
\end{proof}

\begin{lemma}\label{lemma:subset-property}
%If $T_1$ is a subset of $T_2$, 
If $T_1 \subseteq T_2$, then for any maximal $G$-connected subsequence $T_1'$ of $T_1$, we can find a maximal $G$-connected subsequence $T_2'$ of $T_2$ such that %$T_1'$ is a subset of $T_2'$.
$T_1' \subseteq T_2'$.
\end{lemma}
\begin{proof}
 \vspace{-0.5em}
Since $T_1' \subseteq T_1 \subseteq T_2 $, we know $T_1'$ is a $G$-connected subsequence of $T_2$. Based on Lemma~\ref{lemma:union-property}, we can find a maximal $G$-connected subsequence of $T_2$, denoted by $T_2'$, such that $T_1'\cap T_2'\neq \emptyset$. If there exists a timestamp $T_1'[x]$ such that $T_1'[x]\notin T_2'$, similar to the proof of case (1) in Lemma~\ref{lemma:union-property}, we can obtain a contradiction. Thus, all the timestamps in $T_1'$ must occur in $T_2'$.
\end{proof}

@@

\begin{example}
Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a decomposable sequence
because one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
In contrast, $T_2$ is a decomposable sequence because the sequence itself is the maximal $2$-connected subsequence, which is also $2$-consecutive and with size no smaller than than $4$.
\end{example}

@@

\begin{proof}
 \vspace{-0.5em}
It is obvious that $\mathtt{sim}(T)$ is a one-to-one function. Given an input sequence T, there is a unique  $\mathtt{sim}(T)$. Let $T_p$ be a decomposable subset of $T$ and we prove the lemma by showing that $\mathtt{sim}(T)$ is a superset of $T_p$.

@@

\begin{proof}
 \vspace{-0.5em}
We prove by contradiction. Suppose there exists a valid pattern $P_2$ such that $P_2.O \supseteq P.O$. It is obvious that $P_2.T \subseteq P.T$. Based on Definition 2, the following conditions hold: (1) $P_2.T$ is $G$-connected. (2) $|P_2.T| \geq K$ and (3) $P_2.T$ is $L$-consecutive. Note that the entire $P_2.T$ is $G$-connected. Thus, $P_2.T$ itself is the only maximal $G$-connected subsequence. Based on conditions (1),(2),(3) and Definition 6, $P_2.T$ is decomposable. Then, based on Lemma~\ref{lemma:decom-sim}, we know $\mathtt{sim}(T)\neq \emptyset$ because $P_2.T \subseteq P.T$ and $P_2.T$ is decomposable. This leads to a contradiction with $\mathtt{sim}(P.T)=\emptyset$.
\end{proof}

@@

Our customized Apriori Enumerator is presented in Algorithm~\ref{algo:apriori_mining}. Initially, the edges (pairs of objects) in the star constitute the bottom level (Lines~\ref{code:init-start}-\ref{code:init-end}) and invalid candidates are excluded (Line~\ref{code:simp1}). An indicator \emph{level} is used to control the result size for candidate joins. During each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}), only candidates with object size equals to \emph{level} are generated (Line~\ref{code:join-start}). When two candidates $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Lines~\ref{code:join}). To check the validity of the candidate, we calculate $\mathtt{sim}(c'.T)$. If its simplified sequence is empty, $c'$ is excluded from the next level (Line~\ref{code:simp2}). This ensures that all the candidates with $P.O\supseteq c'.O$ are pruned. If a candidate cannot generate any new candidate, the
it is directly reported (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+,pei2000closet} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}). If yes, we can early terminate the algorithm and output the results.

@@

\subsection{Put Everything Together}
We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, for ease of presentation, we used an aggregated graph $G_A$ to capture the clustering relationship. However, in the implementation of the map phase, there is no need to create $G_A$ in advance. Instead, we simply need to emit the edges within a star to the same reducer. 
%Before sending stars to reducers, we use a simple best-fit strategy to calculate the star allocation. Under the best-fit strategy, the most costly unallocated star is assigned to the most lightly loaded reducers, where we use the edges in the star as a cost estimation.
Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a candidate pattern $\langle o,i: e(o,i) \rangle$ is created. Then it enumerates all the valid patterns from the candidate patterns. The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.  
In Apache Spark, further optimization can be made by balancing the loads among reducers at runtime. 
Leveraging
Spark's DAG execution engine~\cite{zaharia2012resilient}, a planning phase can be inserted in between map and reduce phases.
With knowing all map results (i.e., star sizes), a simple best-fit planning strategy can be adopted by assigning the most costly unallocated star to the most lightly loaded reducer, where the edges in a star can be used as a cost estimation.

@@

Compared with TRPM, the SPARE framework does not rely on snapshot replication to guarantee correctness. In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
\begin{theorem}[Pattern Uniqueness]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
\end{theorem}
\begin{proof} \vspace{-0.5em}
We prove by contradiction. Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set. Note that the center vertex of the star is associated with the minimum id. Let $o_i$ and $o_j$ be the center vertexes of the two partitions and we have $o_i=o_j$. However, $P_i$ and $P_j$ are different stars, meaning their center vertexes are different (i.e., $o_i\neq o_j$), leading to a contradiction. 
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}  \vspace{-0.5em}
See Appendix~\ref{apx:spm_correct}.
\end{proof}

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.85\textwidth]{spm.eps}
\vspace{-0.5em}
\caption{Star Partitioning and ApRiori Enumerator (SPARE). (a) Aggregated graph $G_A$ generated from Figure 1. (b) Five star partitions are generated from $G_A$. Star IDs are circled, vertexes and inverted lists are in the connected tables.
(c) Apriori Enumerator with various pruning techniques.}
\label{fig:star_partition}
\vspace{-0.5em}
\end{figure*}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{star-alt.eps}
\vspace{-0.5em}
\caption{Star partitioning with different vertex orderings.}
\vspace{-0.5em}
\label{fig:star-alt}
\end{figure}

@@

The maximal $G$-connected subsequence has the following two properties:
\begin{lemma}\label{lemma:union-property}
Suppose $\{T_1,T_2,\ldots,T_m\}$ is the set of all maximal $G$-connected subsequences of $T$, we have (1) $T_i\cap T_j=\emptyset$ for $i\neq j$ and (2) $T_1\cup T_2\cup\ldots\cup T_m=T$.
\end{lemma}
\begin{proof}
 %\vspace{-0.5em}
We assume $T_i\cap T_j\neq \emptyset$. Let $T_i=(T_i[1], T_i[2],\ldots,T_i[p])$ and $T_j= (T_j[1], T_j[2],\ldots,T_j[n])$. Suppose $T[x]$ is a timestamp occurring in both $T_i$ and $T_j$. Let $T[y]=\min\{T_i[1],T_j[1]\}$, i.e., the minimum timestamp of $T_i[1]$ and $T_j[1]$ occurs at the $y$-th position of sequence $T$. Similarly, we assume $T[z]=\max\{T_i[p], T_j[n]\}$. Apparently, the two subsequences $T[y:x]$ and $T[x:z]$ are $G$-connected because $T_i$ and $T_j$ are both $G$-connected. Then, sequence $(T_y,\ldots,T_x,\ldots,T_z)$, the superset of $T_i$ and $T_j$, is also $G$-connected. This contradicts with the assumptions that $T_i$ and $T_j$ are maximal $G$-connected subsequences.

To prove (2), we assume $\cup_{i=1}^{i=m} T_i$ does not cover all the timestamps in $T$. Then, we can find a subsequence $T'=T[x:x+t]$ such that $T[x-1]\in T_a$ $(1\leq a\leq m)$, $T[x+t+1]\in T_b$ $(1\leq b\leq m)$ and all the timestamps in $T'$ is not included in any $T_i$. Let $g'=\min\{T[x]-T[x-1], T[x+t+1]-T[x+t]\}$. If $g'\leq G$, then it is easy to infer that $T_a$ or $T_b$ is not a maximal $G$-connected subsequence because we can combine it with $T[x]$ or $T[x+t]$  to form a superset which is also $G$-connected. If $g'>G$, $T'$ itself is a maximal $G$-connected subsequence which is missed in $\cup_{i=1}^{i=m} T_i$. Both cases lead to contradictions.
\end{proof}

\begin{lemma}\label{lemma:subset-property}
%If $T_1$ is a subset of $T_2$, 
If $T_1 \subseteq T_2$, then for any maximal $G$-connected subsequence $T_1'$ of $T_1$, we can find a maximal $G$-connected subsequence $T_2'$ of $T_2$ such that %$T_1'$ is a subset of $T_2'$.
$T_1' \subseteq T_2'$.
\end{lemma}
\begin{proof}
 %\vspace{-0.5em}
Since $T_1' \subseteq T_1 \subseteq T_2 $, we know $T_1'$ is a $G$-connected subsequence of $T_2$. Based on Lemma~\ref{lemma:union-property}, we can find a maximal $G$-connected subsequence of $T_2$, denoted by $T_2'$, such that $T_1'\cap T_2'\neq \emptyset$. If there exists a timestamp $T_1'[x]$ such that $T_1'[x]\notin T_2'$, similar to the proof of case (1) in Lemma~\ref{lemma:union-property}, we can obtain a contradiction. Thus, all the timestamps in $T_1'$ must occur in $T_2'$.
\end{proof}

@@

\begin{example}
Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a decomposable sequence
because one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
In contrast, $T_2$ is a decomposable sequence because the sequence itself is the maximal $2$-connected subsequence, which is also $2$-consecutive and with size no smaller than $4$.
\end{example}

@@

\begin{proof}
 %\vspace{-0.5em}
It is obvious that $\mathtt{sim}(T)$ is a one-to-one function. Given an input sequence T, there is a unique  $\mathtt{sim}(T)$. Let $T_p$ be a decomposable subset of $T$ and we prove the lemma by showing that $\mathtt{sim}(T)$ is a superset of $T_p$.

@@

\begin{proof}
%\vspace{-0.5em}
We prove by contradiction. Suppose there exists a valid pattern $P_2$ such that $P_2.O \supseteq P.O$. It is obvious that $P_2.T \subseteq P.T$. Based on Definition 2, the following conditions hold: (1) $P_2.T$ is $G$-connected. (2) $|P_2.T| \geq K$ and (3) $P_2.T$ is $L$-consecutive. Note that the entire $P_2.T$ is $G$-connected. Thus, $P_2.T$ itself is the only maximal $G$-connected subsequence. Based on conditions (1),(2),(3) and Definition 6, $P_2.T$ is decomposable. Then, based on Lemma~\ref{lemma:decom-sim}, we know $\mathtt{sim}(T)\neq \emptyset$ because $P_2.T \subseteq P.T$ and $P_2.T$ is decomposable. This leads to a contradiction with $\mathtt{sim}(P.T)=\emptyset$.
\end{proof}

@@

Our customized Apriori Enumerator is presented in Algorithm~\ref{algo:apriori_mining}. Initially, the edges (pairs of objects) in the star constitute the bottom level (Lines~\ref{code:init-start}-\ref{code:init-end}) and invalid candidates are excluded (Line~\ref{code:simp1}). An indicator \emph{level} is used to control the result size for candidate joins. During each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}), only candidates with object size equals to \emph{level} are generated (Line~\ref{code:join-start}). When two candidates $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Lines~\ref{code:join}). To check the validity of the candidate, we calculate $\mathtt{sim}(c'.T)$. If its simplified sequence is empty, $c'$ is excluded from the next level (Line~\ref{code:simp2}). This ensures that all the candidates with $P.O\supseteq c'.O$ are pruned. If a candidate cannot generate any new candidate, then
it is directly reported (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+,pei2000closet} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}). If yes, we can  terminate the algorithm early and output the results.

@@

\subsection{Put Everything Together}
We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, for ease of presentation, we use an aggregated graph $G_A$ to capture the clustering relationship. However, in the implementation of the map phase, there is no need to create $G_A$ in advance. Instead, we simply need to emit the edges within a star to the same reducer. 
%Before sending stars to reducers, we use a simple best-fit strategy to calculate the star allocation. Under the best-fit strategy, the most costly unallocated star is assigned to the most lightly loaded reducers, where we use the edges in the star as a cost estimation.
Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a candidate pattern $\langle o,i: e(o,i) \rangle$ is created. Then it enumerates all the valid patterns from the candidate patterns. The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.  
In Apache Spark, further optimization can be made by balancing the loads among reducers at runtime. 
Leveraging
Spark's DAG execution engine~\cite{zaharia2012resilient}, a planning phase can be inserted in between map and reduce phases.
With knowing all map results (i.e., star sizes), a simple best-fit planning strategy can be adopted by assigning the most costly unallocated star to the most lightly loaded reducer, where the edges in a star can be used as a cost estimation.

@@

Compared with TRPM, the SPARE framework does not rely on snapshot replication to guarantee correctness. In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
\begin{theorem}[Pattern Uniqueness]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
\end{theorem}
\begin{proof} 
\vspace{-0.5em}
We prove by contradiction. Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set. Note that the center vertex of the star is associated with the minimum id. Let $o_i$ and $o_j$ be the center vertexes of the two partitions and we have $o_i=o_j$. However, $P_i$ and $P_j$ are different stars, meaning their center vertexes are different (i.e., $o_i\neq o_j$), leading to a contradiction. 
\vspace{-0.5em}
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}  
\vspace{-0.5em}
See Appendix~\ref{apx:spm_correct}.
\vspace{-0.5em}
\end{proof}
